---
title: "conditionals_loops"
format: html
editor: visual
---

#### Task 1 
Create an object called pm2_5
```{r}
pm2_5 <- 48
```

Now lets make an if else for whats safe

```{r}
if (pm2_5 < 100){
  print("Low to moderate risk")
}else if (pm2_5>= 100 & pm2_5 <150){
  print("Unhealthy for sensitive groups")
}else if (pm2_5 >= 150){
  print("Health risk present")
}
```

#### Task 2
Ok we are going to save some species and see which are blue whales!!

```{r}
species <- "grey whale"

#Ok now we make the if statement
if(stringr::str_detect(species, "whale")){ #detect string "whale" in species 
  print("you found a whale")
} else {
  print("you didnt find shit")
}

```
That works great

#### Task 3
oh cool here we do price changes

```{r}
base_burrito <- 6.5

main_ingredient <- "veggie"
main_ingredient <- "steak"
main_ingredient <- "chicken"

```
ok now we need an if statement for the change in price based on main ingredient

```{r}
if (main_ingredient == "veggie"){
  print(base_burrito)
}else if (main_ingredient == "chicken"){
  print(base_burrito + 3)
}else if (main_ingredient == "steak"){
  print(base_burrito + 3.25)
}
```

#### Task 4 (Usingfor)

First we create a new vector called fish 

```{r}
fish_vals <- c(8,10,12,23)

fish_types <- c("goldfish", "tetras", "guppies", "mollies") #this might be unnecesary 
#lets rawdog this for loop 

fish <- c(goldfish = 8, tetras = 10, guppies = 12, mollies = 23)
```

```{r}
for (i in seq_along(fish)) {
  print(fish[i]/53)
}
```

#### Task 5 
Theres already a vector called month.name
```{r}
month.name
```
oh this is so lit we're going through and printing each month is __

```{r}
#making for loop 
for (i in seq_along(month.name)) {
  print(paste(month.name[i],"is month",i))
}
```
that was the easiest for me tbh 


